An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-17 paper.tex
Added acknowledgements for Anne, Sabrina, Brad, and Dan.

\section*{Acknowledgments}
We thank Roman Boychuk and Obinna Nwanna for assistance with the experiments.

>>>>

\section*{Acknowledgments}
%
We thank Roman Boychuk and Obinna Nwanna for assistance with the experiments.
We also thank Sabrina Abram, Brad Humphreys, and Anne Koelewijn for reviewing
the preprint and being our guinea pigs on the software/data instructions. Dan
Simon also gave valuable feedback on the preprint.
